Comparing Predicted Boundaries vs Called Boundaries

### 2019-08-28 Scripts/comparing_predicted_boundaries_vs_called_boundaries.Rmd
changed formatting of heatmaps; increase fonts

EnrichedHeatmap(mat_pred_ctcf, 
                col = c("black",colorRampPalette(c("white", "pink", "red"))(99)), 
                #heatmap_legend_param = list(show_heatmap_legend = FALSE),
                row_title="Chromosomes",show_heatmap_legend = FALSE,
                row_title_side="left", 
                column_title="Predicted", 
                axis_name = axis_names,
                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col ="red", 
                                                                                   lwd = 2), 
                                                                         yaxis_side = "right", 
                                                                         yaxis_facing = "left")))
```

@@

EnrichedHeatmap(mat_called_ctcf, 
                col = c("black",colorRampPalette(c("white", "pink", "red"))(99)), 
                #heatmap_legend_param = list(show_heatmap_legend = FALSE),
                row_title="Chromosomes",show_heatmap_legend = FALSE,
                row_title_side="left", 
                column_title="Called", 
                axis_name = axis_names,
                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "red", 
                                                                                   lwd = 2,
                                                                                   lty=3), 
                                                                         yaxis_side = "right", 
                                                                         yaxis_facing = "left")))
```

@@

EnrichedHeatmap(mat_pred_rad21, 
                col = c("black",colorRampPalette(c("white", "pink", "red"))(99)), 
                #heatmap_legend_param = list(show_heatmap_legend = FALSE),
                row_title="Chromosomes",show_heatmap_legend = FALSE,
                row_title_side="left", 
                column_title="Predicted", 
                axis_name = axis_names,
                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "red", 
                                                                                   lwd = 2), 
                                                                         yaxis_side = "right", 
                                                                         yaxis_facing = "left")))
```

@@

EnrichedHeatmap(mat_called_rad21, 
                col = c("black",colorRampPalette(c("white", "pink", "red"))(99)), 
                #heatmap_legend_param = list(show_heatmap_legend = FALSE),
                row_title="Chromosomes",show_heatmap_legend = FALSE,
                row_title_side="left", 
                column_title="Called", 
                axis_name = axis_names,
                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "red", 
                                                                                   lwd = 2,
                                                                                   lty = 3), 
                                                                         yaxis_side = "right", 
                                                                         yaxis_facing = "left")))
```

@@

EnrichedHeatmap(mat_pred_smc3, 
                col = c("black",colorRampPalette(c("white", "pink", "red"))(99)), 
                #heatmap_legend_param = list(show_heatmap_legend = FALSE),
                row_title="Chromosomes",show_heatmap_legend = FALSE,
                row_title_side="left", 
                column_title="Predicted", 
                axis_name = axis_names,
                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "red", 
                                                                                   lwd = 2), 
                                                                         yaxis_side = "right", 
                                                                         yaxis_facing = "left")))
```

@@

EnrichedHeatmap(mat_called_smc3, 
                col = c("black",colorRampPalette(c("white", "pink", "red"))(99)), 
                #heatmap_legend_param = list(show_heatmap_legend = FALSE),
                row_title="Chromosomes",show_heatmap_legend = FALSE,
                row_title_side="left", 
                column_title="Called", 
                axis_name = axis_names,
                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "red", 
                                                                                   lwd = 2,
                                                                                   lty = 3), 
                                                                         yaxis_side = "right", 
                                                                         yaxis_facing = "left")))
```

@@

EnrichedHeatmap(mat_pred_znf143, 
                col = c("black",colorRampPalette(c("white", "pink", "red"))(99)), 
                #heatmap_legend_param = list(show_heatmap_legend = FALSE),
                row_title="Chromosomes",show_heatmap_legend = FALSE,
                row_title_side="left", 
                column_title="Predicted", 
                axis_name = axis_names,
                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "red", 
                                                                                   lwd = 2), 
                                                                         yaxis_side = "right", 
                                                                         yaxis_facing = "left")))
```

@@

EnrichedHeatmap(mat_called_znf143, 
                col = c("black",colorRampPalette(c("white", "pink", "red"))(99)), 
                #heatmap_legend_param = list(show_heatmap_legend = FALSE),
                row_title="Chromosomes",show_heatmap_legend = FALSE,
                row_title_side="left", 
                column_title="Called", 
                axis_name = axis_names,
                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "red", 
                                                                                   lwd = 2,
                                                                                   lty = 3), 
                                                                         yaxis_side = "right", 
                                                                         yaxis_facing = "left")))
```

@@

EnrichedHeatmap(mat_pred_ctcf, 
                col = c("black",colorRampPalette(c("white", "lightblue", "blue"))(99)), 
                #heatmap_legend_param = list(show_heatmap_legend = FALSE),
                row_title="Chromosomes",show_heatmap_legend = FALSE,
                row_title_side="left", 
                column_title="Predicted", 
                axis_name = axis_names,
                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col ="blue", 
                                                                                   lwd = 2), 
                                                                         yaxis_side = "right", 
                                                                         yaxis_facing = "left")))
```

@@

EnrichedHeatmap(mat_called_ctcf, 
                col = c("black",colorRampPalette(c("white", "lightblue", "blue"))(99)), 
                #heatmap_legend_param = list(show_heatmap_legend = FALSE),
                row_title="Chromosomes",show_heatmap_legend = FALSE,
                row_title_side="left", 
                column_title="Called", 
                axis_name = axis_names,
                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "blue", 
                                                                                   lwd = 2,
                                                                                   lty=3), 
                                                                         yaxis_side = "right", 
                                                                         yaxis_facing = "left")))
```

@@

EnrichedHeatmap(mat_pred_rad21, 
                col = c("black",colorRampPalette(c("white", "lightblue", "blue"))(99)), 
                #heatmap_legend_param = list(show_heatmap_legend = FALSE),
                row_title="Chromosomes",show_heatmap_legend = FALSE,
                row_title_side="left", 
                column_title="Predicted", 
                axis_name = axis_names,
                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "blue", 
                                                                                   lwd = 2), 
                                                                         yaxis_side = "right", 
                                                                         yaxis_facing = "left")))
```

@@

EnrichedHeatmap(mat_called_rad21, 
                col = c("black",colorRampPalette(c("white", "lightblue", "blue"))(99)), 
                #heatmap_legend_param = list(show_heatmap_legend = FALSE),
                row_title="Chromosomes",show_heatmap_legend = FALSE,
                row_title_side="left", 
                column_title="Called", 
                axis_name = axis_names,
                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "blue", 
                                                                                   lwd = 2,
                                                                                   lty = 3), 
                                                                         yaxis_side = "right", 
                                                                         yaxis_facing = "left")))
```

@@

EnrichedHeatmap(mat_pred_smc3, 
                col = c("black",colorRampPalette(c("white", "lightblue", "blue"))(99)), 
                #heatmap_legend_param = list(show_heatmap_legend = FALSE),
                row_title="Chromosomes",show_heatmap_legend = FALSE,
                row_title_side="left", 
                column_title="Predicted", 
                axis_name = axis_names,
                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "blue", 
                                                                                   lwd = 2), 
                                                                         yaxis_side = "right", 
                                                                         yaxis_facing = "left")))
```

@@

EnrichedHeatmap(mat_called_smc3, 
                col = c("black",colorRampPalette(c("white", "lightblue", "blue"))(99)), 
                #heatmap_legend_param = list(show_heatmap_legend = FALSE),
                row_title="Chromosomes",show_heatmap_legend = FALSE,
                row_title_side="left", 
                column_title="Called", 
                axis_name = axis_names,
                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "blue", 
                                                                                   lwd = 2,
                                                                                   lty = 3), 
                                                                         yaxis_side = "right", 
                                                                         yaxis_facing = "left")))
```

@@

EnrichedHeatmap(mat_pred_znf143, 
                col = c("black",colorRampPalette(c("white", "lightblue", "blue"))(99)), 
                #heatmap_legend_param = list(show_heatmap_legend = FALSE),
                row_title="Chromosomes",show_heatmap_legend = FALSE,
                row_title_side="left", 
                column_title="Predicted", 
                axis_name = axis_names,
                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "blue", 
                                                                                   lwd = 2), 
                                                                         yaxis_side = "right", 
                                                                         yaxis_facing = "left")))
```

@@

EnrichedHeatmap(mat_called_znf143, 
                col = c("black",colorRampPalette(c("white", "lightblue", "blue"))(99)), 
                #heatmap_legend_param = list(show_heatmap_legend = FALSE),
                row_title="Chromosomes",show_heatmap_legend = FALSE,
                row_title_side="left", 
                column_title="Called", 
                axis_name = axis_names,
                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "blue", 
                                                                                   lwd = 2,
                                                                                   lty = 3), 
                                                                         yaxis_side = "right", 
                                                                         yaxis_facing = "left")))
```

>>>>

EnrichedHeatmap(mat_pred_ctcf, 
                col = c("black",colorRampPalette(c("white", "green", "darkgreen"))(99)), 
                #heatmap_legend_param = list(show_heatmap_legend = FALSE),
                row_title="Chromosomes",show_heatmap_legend = FALSE,
                row_title_side="left", 
                column_title="Predicted", 
                axis_name = axis_names,
				column_title_gp = gpar(fontsize = 20),
				row_title_gp = gpar(fontsize = 20),
				axis_name_gp = gpar(fontsize = 20),
                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col ="darkgreen", fontsize = 10,
                                                                                   lwd = 2), 
                                                                         yaxis_side = "right", 
                                                                         yaxis_facing = "left")))

@@

EnrichedHeatmap(mat_called_ctcf, 
                col = c("black",colorRampPalette(c("white", "lightblue", "blue"))(99)), 
                #heatmap_legend_param = list(show_heatmap_legend = FALSE),
                row_title="Chromosomes",show_heatmap_legend = FALSE,
                row_title_side="left", 
                column_title="Called", 
                axis_name = axis_names,
				column_title_gp = gpar(fontsize = 20),
				row_title_gp = gpar(fontsize = 20),
				axis_name_gp = gpar(fontsize = 20),
                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "blue", 
                                                                                   lwd = 2), 
                                                                         yaxis_side = "right", 
                                                                         yaxis_facing = "left")))
```

@@

EnrichedHeatmap(mat_pred_rad21, 
                col = c("black",colorRampPalette(c("white", "green", "darkgreen"))(99)), 
                #heatmap_legend_param = list(show_heatmap_legend = FALSE),
                row_title="Chromosomes",show_heatmap_legend = FALSE,
                row_title_side="left", 
                column_title="Predicted", 
                axis_name = axis_names,
				column_title_gp = gpar(fontsize = 20),
				row_title_gp = gpar(fontsize = 20),
				axis_name_gp = gpar(fontsize = 20),
                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "darkgreen", 
                                                                                   lwd = 2), 
                                                                         yaxis_side = "right", 
                                                                         yaxis_facing = "left")))

@@

EnrichedHeatmap(mat_called_rad21, 
                col = c("black",colorRampPalette(c("white", "lightblue", "blue"))(99)), 
                #heatmap_legend_param = list(show_heatmap_legend = FALSE),
                row_title="Chromosomes",show_heatmap_legend = FALSE,
                row_title_side="left", 
                column_title="Called", 
                axis_name = axis_names,
				column_title_gp = gpar(fontsize = 20),
				row_title_gp = gpar(fontsize = 20),
				axis_name_gp = gpar(fontsize = 20),
                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "blue", 
                                                                                   lwd = 2), 
                                                                         yaxis_side = "right", 
                                                                         yaxis_facing = "left")))

@@

EnrichedHeatmap(mat_pred_smc3, 
                col = c("black",colorRampPalette(c("white", "green", "darkgreen"))(99)), 
                #heatmap_legend_param = list(show_heatmap_legend = FALSE),
                row_title="Chromosomes",show_heatmap_legend = FALSE,
                row_title_side="left", 
                column_title="Predicted", 
                axis_name = axis_names,
				column_title_gp = gpar(fontsize = 20),
				row_title_gp = gpar(fontsize = 20),
				axis_name_gp = gpar(fontsize = 20),
                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "darkgreen", 
                                                                                   lwd = 2), 
                                                                         yaxis_side = "right", 
                                                                         yaxis_facing = "left")))

@@

EnrichedHeatmap(mat_called_smc3, 
                col = c("black",colorRampPalette(c("white", "lightblue", "blue"))(99)), 
                #heatmap_legend_param = list(show_heatmap_legend = FALSE),
                row_title="Chromosomes",show_heatmap_legend = FALSE,
                row_title_side="left", 
                column_title="Called", 
                axis_name = axis_names,
				column_title_gp = gpar(fontsize = 20),
				row_title_gp = gpar(fontsize = 20),
				axis_name_gp = gpar(fontsize = 20),
                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "blue", 
                                                                                   lwd = 2), 
                                                                         yaxis_side = "right", 
                                                                         yaxis_facing = "left")))

@@

EnrichedHeatmap(mat_pred_znf143, 
                col = c("black",colorRampPalette(c("white", "green", "darkgreen"))(99)), 
                #heatmap_legend_param = list(show_heatmap_legend = FALSE),
                row_title="Chromosomes",show_heatmap_legend = FALSE,
                row_title_side="left", 
                column_title="Predicted", 
                axis_name = axis_names,
				column_title_gp = gpar(fontsize = 20),
				row_title_gp = gpar(fontsize = 20),
				axis_name_gp = gpar(fontsize = 20),
                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "darkgreen", 
                                                                                   lwd = 2), 
                                                                         yaxis_side = "right", 
                                                                         yaxis_facing = "left")))

@@

EnrichedHeatmap(mat_called_znf143, 
                col = c("black",colorRampPalette(c("white", "lightblue", "blue"))(99)), 
                #heatmap_legend_param = list(show_heatmap_legend = FALSE),
                row_title="Chromosomes",show_heatmap_legend = FALSE,
                row_title_side="left", 
                column_title="Called", 
                axis_name = axis_names,
				column_title_gp = gpar(fontsize = 20),
				row_title_gp = gpar(fontsize = 20),
				axis_name_gp = gpar(fontsize = 20),
                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "blue", 
                                                                                   lwd = 2), 
                                                                         yaxis_side = "right", 
                                                                         yaxis_facing = "left")))

@@

EnrichedHeatmap(mat_pred_ctcf, 
                col = c("black",colorRampPalette(c("white", "green", "darkgreen"))(99)), 
                #heatmap_legend_param = list(show_heatmap_legend = FALSE),
                row_title="Chromosomes",show_heatmap_legend = FALSE,
                row_title_side="left", 
                column_title="Predicted", 
                axis_name = axis_names,
				column_title_gp = gpar(fontsize = 20),
				row_title_gp = gpar(fontsize = 20),
				axis_name_gp = gpar(fontsize = 20),
                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col ="darkgreen", fontsize = 10,
                                                                                   lwd = 2), 
                                                                         yaxis_side = "right", 
                                                                         yaxis_facing = "left")))

@@

EnrichedHeatmap(mat_called_ctcf, 
                col = c("black",colorRampPalette(c("white", "lightblue", "blue"))(99)), 
                #heatmap_legend_param = list(show_heatmap_legend = FALSE),
                row_title="Chromosomes",show_heatmap_legend = FALSE,
                row_title_side="left", 
                column_title="Called", 
                axis_name = axis_names,
				column_title_gp = gpar(fontsize = 20),
				row_title_gp = gpar(fontsize = 20),
				axis_name_gp = gpar(fontsize = 20),
                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "blue", 
                                                                                   lwd = 2), 
                                                                         yaxis_side = "right", 
                                                                         yaxis_facing = "left")))

@@

EnrichedHeatmap(mat_pred_rad21, 
                col = c("black",colorRampPalette(c("white", "green", "darkgreen"))(99)), 
                #heatmap_legend_param = list(show_heatmap_legend = FALSE),
                row_title="Chromosomes",show_heatmap_legend = FALSE,
                row_title_side="left", 
                column_title="Predicted", 
                axis_name = axis_names,
				column_title_gp = gpar(fontsize = 20),
				row_title_gp = gpar(fontsize = 20),
				axis_name_gp = gpar(fontsize = 20),
                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "darkgreen", 
                                                                                   lwd = 2), 
                                                                         yaxis_side = "right", 
                                                                         yaxis_facing = "left")))

@@

EnrichedHeatmap(mat_called_rad21, 
                col = c("black",colorRampPalette(c("white", "lightblue", "blue"))(99)), 
                #heatmap_legend_param = list(show_heatmap_legend = FALSE),
                row_title="Chromosomes",show_heatmap_legend = FALSE,
                row_title_side="left", 
                column_title="Called", 
                axis_name = axis_names,
				column_title_gp = gpar(fontsize = 20),
				row_title_gp = gpar(fontsize = 20),
				axis_name_gp = gpar(fontsize = 20),
                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "blue", 
                                                                                   lwd = 2), 
                                                                         yaxis_side = "right", 
                                                                         yaxis_facing = "left")))

@@

EnrichedHeatmap(mat_pred_smc3, 
                col = c("black",colorRampPalette(c("white", "green", "darkgreen"))(99)), 
                #heatmap_legend_param = list(show_heatmap_legend = FALSE),
                row_title="Chromosomes",show_heatmap_legend = FALSE,
                row_title_side="left", 
                column_title="Predicted", 
                axis_name = axis_names,
				column_title_gp = gpar(fontsize = 20),
				row_title_gp = gpar(fontsize = 20),
				axis_name_gp = gpar(fontsize = 20),
                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "darkgreen", 
                                                                                   lwd = 2), 
                                                                         yaxis_side = "right", 
                                                                         yaxis_facing = "left")))

@@

EnrichedHeatmap(mat_called_smc3, 
                col = c("black",colorRampPalette(c("white", "lightblue", "blue"))(99)), 
                #heatmap_legend_param = list(show_heatmap_legend = FALSE),
                row_title="Chromosomes",show_heatmap_legend = FALSE,
                row_title_side="left", 
                column_title="Called", 
                axis_name = axis_names,
				column_title_gp = gpar(fontsize = 20),
				row_title_gp = gpar(fontsize = 20),
				axis_name_gp = gpar(fontsize = 20),
                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "blue", 
                                                                                   lwd = 2), 
                                                                         yaxis_side = "right", 
                                                                         yaxis_facing = "left")))

@@

EnrichedHeatmap(mat_pred_znf143, 
                col = c("black",colorRampPalette(c("white", "green", "darkgreen"))(99)), 
                #heatmap_legend_param = list(show_heatmap_legend = FALSE),
                row_title="Chromosomes",show_heatmap_legend = FALSE,
                row_title_side="left", 
                column_title="Predicted", 
                axis_name = axis_names,
				column_title_gp = gpar(fontsize = 20),
				row_title_gp = gpar(fontsize = 20),
				axis_name_gp = gpar(fontsize = 20),
                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "darkgreen", 
                                                                                   lwd = 2), 
                                                                         yaxis_side = "right", 
                                                                         yaxis_facing = "left")))

@@

EnrichedHeatmap(mat_called_znf143, 
                col = c("black",colorRampPalette(c("white", "lightblue", "blue"))(99)), 
                #heatmap_legend_param = list(show_heatmap_legend = FALSE),
                row_title="Chromosomes",show_heatmap_legend = FALSE,
                row_title_side="left", 
                column_title="Called", 
                axis_name = axis_names,
				column_title_gp = gpar(fontsize = 20),
				row_title_gp = gpar(fontsize = 20),
				axis_name_gp = gpar(fontsize = 20),
                top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = "blue", 
                                                                                   lwd = 2), 
                                                                         yaxis_side = "right", 
                                                                         yaxis_facing = "left")))
